
%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007

%%%%%%%%%  MCI Project Supervisor Meeting Week 3%%%%%%%%%%
%%%%%%%%% Author: Changchang Liu %%%%%%%%%%%%%%%%%%
%%%%%%%%% 13 March 2017%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent The {\em 6th} MCI Project weekly meeting will be held in {\bf Ingkarni Wardli level 4} at {\bf 2:30 Pm on Tuesday 4 April 2017}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Tianxu Xi           }
\section{Group members}
\begin{itemize}
	\item a1674472  Tianxu Xi
	\item a1692335 Changchang Liu
\end{itemize}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}
\ None \\


%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Summary for last meeting}
\begin {itemize} 
\item We showed our work and progress. 
\item Some questions about how to design add button for trace table.
\item Some questions about how to run gdb command by clicking one button on the page.
\item Review our business case.
\end {itemize}


\section{Summary for this meeting}
\ Tianxu and Changchang will introduce the progress so far and future work in week6. In addition, we will check if our work is enough for the first milestone. \\
%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Our work and progress}
\begin {itemize} 
\item We have already finished establishment of login page and the connection with database. In addition, users can use correct username and password to login, and page will jump to corresponding pages.  
\item Basic student mode page has already been built. On the selectcode page, student can choose code from database and check the summary of code. On the tracetable page, student can add a new row in the trace table by clicking add button. 
\item The basic database has already been built.
\item We can extract all variables by using gdb.
\item Teacher mode has been built basically. Different parts have been arranged well on the different pages.

\end {itemize}
%%%if there are more subissues, make them as subsections.


%%%more issues should make it like the above one.
\section{Questions}
\begin {itemize} 
\item How can we run gdb command by clicking one button on the page?
\end {itemize}

\section{Work for this week}
\ We will discuss how to build a perfect structure of database, how to compare the results with correct answers and still work on the establishment of teacher mode and student mode pages. \\


%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on 11 April 2017.


\end{document}
