%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007

%%%%%%%%%  MCI Project Supervisor Meeting Week 3%%%%%%%%%%
%%%%%%%%% Author: Changchang Liu %%%%%%%%%%%%%%%%%%
%%%%%%%%% 13 March 2017%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent The {\em 8th} MCI Project weekly meeting will be held in {\bf Ingkarni Wardli level 4} at {\bf 2:30 Pm on Tuesday 9 May 2017}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Tianxu Xi           }
\section{Group members}
\begin{itemize}
	\item a1674472  Tianxu Xi
	\item a1692335 Changchang Liu
\end{itemize}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}
\ None \\


%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Summary for last meeting}
\begin {itemize} 
\item We presented our second milestone and showed our progress.
\item Some work for last week has been pointed.
\item Some work for second milestone has been discussed in detail.
\end {itemize}


\section{Summary for this meeting}
\ Tianxu and Changchang will introduce our progress so far and future work. In addition, we will discuss with supervisor and make sure whether there is something else that we should finish for second milestone. \\
%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Our work and progress}
\begin {itemize} 
\item Tianxu has already fixed the design for every page in student mode, especially for zoom issue. 
\item We finished the connection between teacher mode and student mode. The student score can be generated and insert into database.
\item Some reasonable buttons are also added on suitable pages. 

\end {itemize}
%%%if there are more subissues, make them as subsections.

\section{Teacher mode}
\ Changchang will introduce her work and current progress for last week.\\

\section{Student mode}
\ Tianxu will demonstrate the student mode that has been rebuilt.\\


\section{Work for this week}
\ We will work on fixing bugs and think about how to make trace table have more effective functions. \\


%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on 16 May 2017.


\end{document}
