
%%%%%%weekly meeting template, prepared by Michael Sheng.  09/03/2007

%%%%%%%%%  MCI Project Supervisor Meeting Week 3%%%%%%%%%%
%%%%%%%%% Author: Changchang Liu %%%%%%%%%%%%%%%%%%
%%%%%%%%% 13 March 2017%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin -0.5 cm
\evensidemargin -0.5 cm
\textwidth 15 cm
\topmargin -1.2 cm
\textheight 22 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the no, time, and venue of the meeting
\noindent The {\em 4th} MCI Project weekly meeting will be held in {\bf Ingkarni Wardli level 4} at {\bf 2:30 Pm on Tuesday 21 March 2017}.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda
\end{center}



%%%first, nominate a chair for the meeting. We suggest that each member at least has one chance as the chair.
\section*{Chair: Tianxu Xi           }
\section{Group members}
\begin{itemize}
	\item a1674472  Tianxu Xi
	\item a1692335 Changchang Liu
\end{itemize}

%%%if some students cannot make the meeting due to some reasons, their names should appear here.
\section{Apologies}
\ None \\


%%%short presentation about the work of previous week or any milestone specified in the course.
\section{Summary for last meeting}
\begin {itemize} 
\item We have discussed with teachers how to use debugger to pick up all the variables and their values. Supervisor gave us some hints. 
\item Also, we asked how to use PHP to figure out the button problem (how to click multiple times.)
\item Some questions about login interface and connecting database.
\item A little introduction of pitch and how to change structure of our power-point.
\end {itemize}


\section{Summary for this meeting}
\ Tianxu and Changchang will introduce the progress so far and future work in week4. In addition, show the little introduction of pitch this week and how we changed power-point.\\
%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.
\section{Pitch presentation and power-point structure}
\begin {itemize} 
\item Little summary about what we will introduce and who will introduce which parts
\item Background will show audience why we need trace table.(because programming is hard and it is a good practice tool) The function and advantage of it. 
\item Introduction of this project will demonstrate clients the two modes of this tool and how to use it. Some examples will show clients for better understanding.
\item Little introduction about current memory tracer.
\item Significant advantages for our project, why it is better than the current memory tracer.
\item Future improvement about how to make this tool bigger and more functional.
\item Little conclusion about what we present.

\end {itemize}
%%%if there are more subissues, make them as subsections.


%%%more issues should make it like the above one.
\section{Working on GDB}
\ Changchang will introduce the progress about our work on GDB and show the achievements that we did. \\

\section{Work for this week}
\ We will work on database and how to connect it with the local file and the structure of the database.  \\


%%%finally, specifies time of next meeting
\vspace*{10pt}
\noindent Note: Next meeting to be held on 28 March 2017.


\end{document}
