%%%%%%%%% MCI Project group21 Weekly Meeting Minutes - Week 8%%%%%%%%%%
%%%%%%%%% Author: Changchang Liu%%%%%%%%%%%%%%%%%%
%%%%%%%%% 14 March 2017 %%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}


\begin{document}

\title{Minutes for Eighth Supervisor Meeting}
\author{MCI Group21}
\date{Tuesday 2 May 2017}
\maketitle

\vspace*{15pt}

%%% title
\begin{center}
\begin{flushleft}
  \textbf{Chair}      \qquad Changchang Liu\\
  \textbf{Members}
  \begin {itemize}
  		\item a1674472 Tianxu Xi
		\item a1692335 Changchang Liu

  \end{itemize} 
  \textbf{Apologies}  \ None\\
\end{flushleft}
\end{center}



%%%% begin document

\vspace*{10pt}

%%% date, time and place
\section{Time and Place}
The \emph{eighth} supervisor meeting for the MCI Group Project was held in \textbf{Ingkarni Wardli level 4} at \textbf{2:30pm on Tuesday 1st May 2017}.
 
%%% quorum announcement
\section{Quorum Announcement}
The Chairperson announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its business.



%%% minutes


\section{Milestone One}
Our group described our milestone two, and for the second milestone we need to finish the following tasks:
\begin{itemize}
\item Finish the function of score statistic and analysis.
\item Finish the function of Error Analytics.
\item Accomplish basic function of trace table.
\item Finish the basic page design.
\item Connection between student mode and teacher mode.
\end{itemize}

\section{Represent the current achievements for C Tracer}
\subsection{Teacher mode - the function of score statistic and analysis}
Changchang Liu illustrated the current achievements for teachers mode.
\begin{itemize}
\item Can display a table of the overview information about student submit.
\item Can display a table of the statistic information according to filenames and display a pie chart of student’s performance level according to a selected file.
\item Can display a table of the statistic information according to classes and display a pie chart of student’s performance level according to a selected class and a selected file.

\end{itemize}
\subsection{Student mode}
Tianxu illustrated the current achievements for Students mode.
\begin{itemize}
\item Focus on finding the method of mark the students' inputs.
\item Focus on redesign of the web page.
\end{itemize}

\subsection{Issues need to be fixed}
\begin{itemize}
\item Have to put the diagram of performance level behind of the detailed table.
\item Have to change the value of some buttons.
\item Have to delete the 'filename' from the score table according to a selected class.
\item Have to solve the scaling problem of the web page.
\item Need to mark student according to the percentage of error and correct lines.
\item Need to focus on connect between teacher and student mode.
\end{itemize}



%%% adjournment
\section{Adjournment}
The next meeting is a \emph{Supervisor} meeting with all members present, and will be held in \emph{Ingkarni Wardli Level 4} at \emph{2:30pm} on \emph{9 May, 2017}.



\end{document}

