%%%%%%%%% MCI Project group21 Weekly Meeting Minutes - Week 9%%%%%%%%%%
%%%%%%%%% Author: TianxuXi%%%%%%%%%%%%%%%%%%
%%%%%%%%% 9 May 2017 %%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}


\begin{document}

\title{Minutes of 8th Meeting with Supervisor}
\author{MCI Team21}
\date{Tuesday 9 May 2017}
\maketitle

\vspace*{15pt}

%%% title
\begin{center}
\begin{flushleft}
  \textbf{Chair}      \qquad Tianxu Xi\\
  \textbf{Secretary}   \qquad Tianxu Xi\\
  \textbf{Group Members}
  \begin {itemize}
  		\item a1674472 Tianxu Xi
		\item a1692335 Changchang Liu

  \end{itemize} 
  \textbf{Apologies}  \ None\\
\end{flushleft}
\end{center}



%%%% begin document

\vspace*{10pt}

%%% date, time and place
\section{Time and Place}
The \emph{8th} group meeting with supervisor for the MCI Group Project was held in \textbf{Ingkarni Wardli level 4} at \textbf{2:30pm on Tuesday 9th May 2017}.
 
%%% quorum announcement
\section{Quorum Announcement}
The Chairperson announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its business.

\section{Summary of previous meeting}
Supervisor discussed with us about milestone two in detail and confirmed every definite part. In addition, we also received some effective advises from supervisor and understood what we needed to do last week.

\section{Content of this meeting}
%%% minutes
\subsection{Student mode}
\begin{itemize}
\item Every field in trace table should be highlighted by colors.(green means right, red means wrong) The tick and cross symbol should also be shown.
\item Tool should show students their scores and get feedback.
\item Students can get hints by clicking wrong answers.
\item "if" and "for" structures should be considered in this tool.
\item Some hints and notices should be added appropriately.

\end{itemize}

\subsection{Login part}
\begin{itemize}
\item Teacher can add new students into database.
\item Student can change their passwords.
\end{itemize}

\subsection{Teacher mode}
\begin{itemize}
\item The pie chart should be changed and became more clearly.
\item Teacher may need to finish addition of statements manually.
\end{itemize}

\subsection{Testing}
\begin{itemize}
\item Supervisor told us some significant point about testing.
\end{itemize}


%%% adjournment
\section{Adjournment}
The next meeting is a \emph{Supervisor} meeting with all members present, and will be held in \emph{Ingkarni Wardli Level 4} at \emph{2:30pm} on \emph{16 May, 2017}.



\end{document}

