%%%%%%%%% MCI Project group21 Weekly Meeting Minutes - Week 5%%%%%%%%%%
%%%%%%%%% Author: Changchang Liu%%%%%%%%%%%%%%%%%%
%%%%%%%%% 14 March 2017 %%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}


\begin{document}

\title{Minutes for Fifth Supervisor Meeting}
\author{MCI Group21}
\date{Tuesday 29 March 2017}
\maketitle

\vspace*{15pt}

%%% title
\begin{center}
\begin{flushleft}
  \textbf{Chair}      \qquad Changchang Liu\\
  \textbf{Members}
  \begin {itemize}
  		\item a1674472 Tianxu Xi
		\item a1692335 Changchang Liu

  \end{itemize} 
  \textbf{Apologies}  \ None\\
\end{flushleft}
\end{center}



%%%% begin document

\vspace*{10pt}

%%% date, time and place
\section{Time and Place}
The \emph{fifth} supervisor meeting for the MCI Group Project was held in \textbf{Ingkarni Wardli level 4} at \textbf{2:30pm on Tuesday 29th March 2017}.
 
%%% quorum announcement
\section{Quorum Announcement}
The Chairperson announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its business.



%%% minutes
\section{Review Pitch Presentation}
Summary of the results of the pitch presentation, and the client asked our group the prepare more sufficient for the next time.

\section{Milestone One}
Our group described our milestone one, and for the first milestone we need to finish the following tasks:
\begin{itemize}
\item Get the right solutions for trace tables.
\item Design web pages.
\item Login interface.
\item Upload source file, solutions and store them in database.
\item Create empty trace table according to source file.
\end{itemize}

\section{Represent the current achievements for C Tracer}
\subsection{Teacher mode}
Changchang Liu illustrated the current achievements for teachers mode.
\begin{itemize}
\item Finish design and develop the main page for upload source file, including show a list of already exists source files, delete this files by name, and choose new files from local computers.
\item Can store the uploaded source files into database.
\item Can generate the solution by asking teachers generate solutions by using terminal.
\item Can store these solutions into database and display them.
\end{itemize}
\subsection{Student mode}
Tianxu illustrated the current achievements for Students mode.
\begin{itemize}
\item Finish the login interface, and can let user login by input user name and password, and can also separate different users by different authorities.
\item Can mainly display the source file.
\item Can mainly to generate empty trace table;
\end{itemize}

\subsection{Issues need to be fixed}
\begin{itemize}
\item Have to better design the front end of all of the pages.
\item Have to find a way, generate the solution automatically(not by terminal).
\item Have to change the way about how teachers delete the source file.
\item Could add register method if still have time later, and think further about the security issues.
\item Need to delete the line break when display the source code.
\item Need to add the "add" button for the trace table to allow students add lines when iterations happen.
\end{itemize}

\section{Check for business case and draft plan(BCDF)}
The supervisor checked both team members BCDF documents and provide some change request for each members, there are some main issues.
\begin{itemize}
\item  Need to be more clearly when describe the project.
\item Need to focus on some  syntax rules for  academic reports.
\item The milestone should be start from week 4 to week 6.
\item The project organization should be more focus on each members tasks.
\item Should be clearly describe all of the milestone tasks.
\end{itemize}


%%% adjournment
\section{Adjournment}
The next meeting is a \emph{Supervisor} meeting with all members present, and will be held in \emph{Ingkarni Wardli Level 4} at \emph{2:30pm} on \emph{4 April, 2017}.



\end{document}

