%%%%%%%%% MCI Project group21 Weekly Meeting Minutes - Week 5%%%%%%%%%%
%%%%%%%%% Author: Changchang Liu%%%%%%%%%%%%%%%%%%
%%%%%%%%% 14 March 2017 %%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}


\begin{document}

\title{Minutes of 6th Meeting with Supervisor}
\author{MCI Team21}
\date{Tuesday 4 April 2017}
\maketitle

\vspace*{15pt}

%%% title
\begin{center}
\begin{flushleft}
  \textbf{Chair}      \qquad Tianxu Xi\\
  \textbf{Secretary}   \qquad Tianxu Xi\\
  \textbf{Group Members}
  \begin {itemize}
  		\item a1674472 Tianxu Xi
		\item a1692335 Changchang Liu

  \end{itemize} 
  \textbf{Apologies}  \ None\\
\end{flushleft}
\end{center}



%%%% begin document

\vspace*{10pt}

%%% date, time and place
\section{Time and Place}
The \emph{6th} group meeting with supervisor for the MCI Group Project was held in \textbf{Ingkarni Wardli level 4} at \textbf{2:30pm on Tuesday 4th April 2017}.
 
%%% quorum announcement
\section{Quorum Announcement}
The Chairperson announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its business.

\section{Summary of previous meeting}
Supervisor reviewed our pitch and gave us some suggestions. In addition, we discussed the design of two modes pages, login page. Finally, supervisor help us look through the draft plan.

\section{Milestone}
%%% minutes
\begin{itemize}
\item we showed our work and progress for milestone.
\item We need to add statements in code summary on trace table page.
\item The results that students fill in should be saved in somewhere by clicking submit button.

\end{itemize}

\section{Some improvemnts}
\subsection{Shell script for gdb}
\begin{itemize}
\item We should try to run our tool in Linux to solve the problems about connection between button and gdb command.
\end{itemize}

\subsection{Interface design}
\begin{itemize}
\item The layout in two modes page should be changed a little.
\end{itemize}


%%% adjournment
\section{Adjournment}
The next meeting is a \emph{Supervisor} meeting with all members present, and will be held in \emph{Ingkarni Wardli Level 4} at \emph{2:30pm} on \emph{11 April, 2017}.



\end{document}

